HPC--101\\Onboarding

### 2022-09-12 hpc_101/sections/03_policies.tex
update to slides
update the slides to contain updated info.

\subsection{Storage Policy}
\begin{frame}
\frametitle{Storage Policy}
\begin{enumerate}
\item ITS is not responsible for any data that is deleted or loss due to user error, hardware failure, administrator error.  Users are responsible for their own data and are highly encouraged to backup data that is important to them at other storage locations
\item Files located on the scratch file systems are subject to a \textbf{10 day} purge policy that is based on the file/directory modified timestamp.  \textbf{Files that are purge cannot be recovered}.  Users are encouraged to copy their results off the scratch file system as soon as possible upon completion of their job
\item  Home storage currently snapshots once a day per user in case of accidental file deletion
\end{enumerate}
\end{frame}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}

@@

\begin{frame}
\frametitle{Where to find all Mana specific policies}
\begin{enumerate}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
\item \href{http://go.hawaii.edu/WSG}{Security}
\item \href{http://go.hawaii.edu/YKG}{For lease storage}
\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
%% \item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
\end{enumerate}
\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}

>>>>

\subsection{Storage Policy}
\begin{frame}
\frametitle{Storage Policy}
\begin{enumerate}
\item ITS is not responsible for any data that is deleted or loss due to user error, hardware failure, administrator error.  Users are responsible for their own data and are highly encouraged to backup data that is important to them at other storage locations
\item Files located on the scratch file systems are subject to a \textbf{20 day} purge policy that is based on the file/directory modified timestamp.  \textbf{Files that are purge cannot be recovered}.  Users are encouraged to copy their results off the scratch file system as soon as possible upon completion of their job
\item  Home storage currently snapshots once a day per user in case of accidental file deletion
\end{enumerate}
\end{frame}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}

@@

%\begin{frame}
%\frametitle{Where to find all Mana specific policies}
%\begin{enumerate}
%%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html\#appendixa}{Chapter 708, Hawaii Revised Statutes}
%%\item \href{http://www.hawaii.edu/infotech/policies/itpolicy.html}{University of Hawaii Executive Policy E2.210}
%\item \href{http://go.hawaii.edu/GSY}{Common systems \& Storage}
%\item \href{http://go.hawaii.edu/0SG}{User Account life cycle}
%\item \href{http://go.hawaii.edu/WSG}{Security}
%\item \href{http://go.hawaii.edu/YKG}{For lease storage}
%\item \href{http://go.hawaii.edu/GK0}{Condo Program \& Off Warranty condo nodes}
%%% \item \href{https://docs.google.com/document/d/1mGcCAsmzGT_hWXLcUNfT2LUwiggCnhqrln32k0IGZZI/}{Special allocations}
%\end{enumerate}
%\end{frame}
%
%\begin{frame}
%\frametitle{Login Node Usage Policy}\footnotesize
%The login nodes are a shared resource and are the only access to the cluster for hundreds of user and are meant to provide the following functionality for all users: 
%\begin{itemize}
%\item Providing ssh shell access 
%\item Facilitate the transfer files to and from the cluster:\\Globus, sftp, scp, rsync
%\item Launching and monitoring SLURM jobs (batch and interactive)
%\item Modifying text files with a text editor: vi/vim, emacs, nano
%\end{itemize}
%\bigskip
%\begin{itemize}
%\item[--] If we identify or are notified that a user is running computation on the login nodes, the application will be killed
%\item[--] If we determine that a user repeatedly violates the login node policy, even after being warned, the repeat offender can have their cluster account disabled
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%\subsection{Lustre Filesystem Purge Policies}
%\begin{frame}
%\frametitle{{\lustre} Filesystem Purge Policies}
%Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have implemented a purge policy.
%
%\begin{itemize}
%\item What in \ctilde/lus/ is subject to the purge policy?
   %\begin{itemize}
   %\item \textbf{Answer:} Everything but directories.
   %\end{itemize}
%\item When will my files be purged?
  %\begin{itemize}  
    %\item \textbf{Answer:} Files greater than or equal to 1 Megabyte in size or are empty (0 bytes) that are 35 days old
    %\item \textbf{Answer:} Files between 1 byte and 1 Megabyte in size that are 120 days old
  %\end{itemize}
%\item What is the age based on?
   %\begin{itemize}
   %\item \textbf{Answer:} Age of file is based on creation time
   %\end{itemize}
   %
%%\item How frequently are files for purged?
%%   \begin{itemize}
%%   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
%%   \end{itemize}
%\end{itemize}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}
%\end{frame}
%
%
%
%\begin{frame}
  %\frametitle{How to check file age for purge}
  %A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
%\begin{semiverbatim}\tiny \texttt
  %$[$root@login-0001 \ctilde$]$\$ age\_check -h
  %
  %Usage:
  %age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]
%
%
  %Options:
%
  %-s -- Sort output
  %
  %-d -- display creation date per file
  %
  %-z -- display size in bytes per file
  %
  %-f -- Do not exclude files between 1 byte and 1 MB
  %
  %-a age -- Lists files that were created at least age days ago (default is 20 days)
  %
  %-p path -- Directory to check in (default is /lus/scratch/root)
%
  %
  %Example:
  %age\_check -a 30  
%
%\end{semiverbatim}
%
%\end{frame}
